The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
fin use \@ref(fig:xyz)

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods (e.g. Carter et al. 2015), whereas social
association represents shared space use by members of the same social group
(Figure 1, Franks et al. 2010). Further, for social interactions or associations
to occur individuals must share space, and thus have overlapping home ranges. In
the context of the social environment, home range overlap is a relatively coarse
scale of sociality across which individuals share space over coarser spatial and
temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction (Castles et al. 2014; Farine 2015). Thus, we
define social scale as the type of social relationship observed that can be
explicitly defined and measured (Farine et al. 2015).

@@

```{r, fig.cap='(ref:spacetime)'}
knitr::include_graphics('../graphics/figure1.png')
```

@@

In general, individuals in multilayer networks became more connected as a
function of social scale, however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed based on ~100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer relevance did not
change for any habitat types or seasons, which suggests habitat-by-season layers
captured most, if not all, of the potential connections and individual would
have across all networks (Figure 3c). Finally, somewhat predictably, graph
strength for winter networks increased up to ~100-200m thresholds, followed by a
plateau, while graph strength for summer networks did not change as the social
threshold increased (Figure 3d).  Taken together, these results suggest the
optimal social scale at which groups should be assigned is likely somewhere
between ~20-100m based on the rate at which network metrics stabilized. For
ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
quantities of data, ~50m is likely an ideal social scale for generating social
networks in caribou and similar species.

@@

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure 4c). Connective redundancy decreased with increasing
landcover resolution due the decrease in connectivity of individuals in winter
forage habitats, resulting in a multilayer network where neighbours were less
frequently repeated in multiple layers (Figure 4b). Layer similarity was
generally stable for forest and open habitats except for a contrasting increase
in similarity for forest and decrease in similarity for open habitats at 250m
landcover resolution (Figure 4a). Layer similarity was not possible to calculate
between winter and summer forage because, at all landcover resolutions greater
than 10m there were no individuals connected in the network layers. <!--
individuals still used forage but in much lower proportion + lowered opportunity
to associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low number of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below ~75 observations for forest, ~210 observations for open
and ~300 observations for forage (Figure 5a). Once sufficient observations were
used, layer similarity stabilized with additional for all three landcover
classes at ~200 observations for forest, ~300 observations for open and forage.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure 5b).
Given the overall trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing the social dynamics across contexts.

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure 6a). Individual graph strength and layer relevance increased for
all summer layers as individuals became more connected with increasing window
lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
length, especially for the summer season, may be resulting in less precisely
defined seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics. Similarly,

@@

In general, individuals in multilayer networks became more connected as a
function of social scale, however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed based on ~100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not
change for any habitat types or seasons, which suggests habitat-by-season layers
captured most, if not all, of the potential connections and individual would
have across all networks (Figure 3c). Finally, somewhat predictably, graph
strength for winter networks increased up to ~100-200m thresholds, followed by a
plateau, while graph strength for summer networks did not change as the social
threshold increased (Figure 3d).  Taken together, these results suggest the
optimal social scale at which groups should be assigned is likely somewhere
between ~20-100m based on the rate at which network metrics stabilized. For
ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
quantities of data, ~50m is likely an ideal social scale for generating social
networks in caribou and similar species.

@@

```{r, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lcres.png')
```

@@

```{r, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-nobs.png')
```

@@

```{r, fig.cap='(ref:winlen)'}
knitr::include_graphics('../graphics/figure-winlength.png')
```

@@

```{r, fig.cap='(ref:winpos)'}
knitr::include_graphics('../graphics/figure-winpos.png')
```

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods (e.g. Carter et al. 2015), whereas social
association represents shared space use by members of the same social group
(Figure \@ref(fig:spacetime), Franks et al. 2010). Further, for social
interactions or associations to occur individuals must share space, and thus
have overlapping home ranges. In the context of the social environment, home
range overlap is a relatively coarse scale of sociality across which individuals
share space over coarser spatial and temporal scales (e.g. Piza-Roca et al.
2018). Although the social environment clearly scales spatially and temporally,
it remains unclear whether coarser scales of sociality, including social
association and home range overlap, vary predictably with social interaction
(Castles et al. 2014; Farine 2015). Thus, we define social scale as the type of
social relationship observed that can be explicitly defined and measured (Farine
et al. 2015).

@@

```{r spacetime, fig.cap='(ref:spacetime)'}
knitr::include_graphics('../graphics/figure1.png')
```

@@

In general, individuals in multilayer networks became more connected as a
function of social scale, however, this relationship varied by habitat type and
season. As social scale increased, connective redundancy increased rapidly when
groups were formed based on ~100m threshold, followed by a plateau and slight
decrease at higher thresholds, presumably due to an increase in summer forest
degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer
relevance did not change for any habitat types or seasons, which suggests
habitat-by-season layers captured most, if not all, of the potential connections
and individual would have across all networks (Figure \@ref(fig:socres)c).
Finally, somewhat predictably, graph strength for winter networks increased up
to ~100-200m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)d).  Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20-100m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is
likely an ideal social scale for generating social networks in caribou and
similar species.

@@

Larger landcover resolution scale resulted in decreased proportion of rare and
patchy habitats and low connectivity of individuals in these habitats. In
winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)c). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers (Figure
\@ref(fig:lcres)b). Layer similarity was generally stable for forest and open
habitats except for a contrasting increase in similarity for forest and decrease
in similarity for open habitats at 250m landcover resolution (Figure
\@ref(fig:lcres)a). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 10m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low number of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below ~75 observations for forest, ~210 observations for open
and ~300 observations for forage (Figure \@ref(fig:nobs)a). Once sufficient
observations were used, layer similarity stabilized with additional for all
three landcover classes at ~200 observations for forest, ~300 observations for
open and forage. Connective redundancy increased with increasing number of
observations as individuals became more connected to neighbours in multiple
layers (Figure \@ref(fig:nobs)b). Given the overall trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing the social dynamics
across contexts.

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)a). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)c, Figure
\@ref(fig:winlen)d). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
Similarly,

@@

@@

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lcres.png')
```

@@

```{r nobs, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-nobs.png')
```

@@

```{r winlen, fig.cap='(ref:winlen)'}
knitr::include_graphics('../graphics/figure-winlength.png')
```

@@

```{r winpos, fig.cap='(ref:winpos)'}
knitr::include_graphics('../graphics/figure-winpos.png')
```
